\acknowledgements

First of all, I would like to thank my thesis advisor, Dr. Virgil Gligor, and reader, Dr. Miao Yu, for providing me with guidance throughout my research. When I focused too much on implementation details, they helped me maintain the big picture of the system.

I would also like to thank CyLab and ECE for providing the hardware used in my research. The different computers I have access to are essential for measuring the compatibility of \XMHF64.

Thank you to Dr. Amit Vasudevan for the insightful discussions about XMHF. These discussions helped me to better understand the security properties and assumptions in the XMHF implementation. Additionally, thank you for taking the time to review my pull requests to XMHF's repository.

I would like to express my gratitude to the instructors of all computer science-related courses I took at UC Davis and CMU. The programming skills I learned in these classes are essential to the success of my research. In particular, I would like to thank Dr. Dave Eckhardt for teaching Operating System Design and Implementation (15-410/605). This class taught me how to efficiently find race conditions in programs, which directly helped me while debugging \XMHF64.

I appreciate the contributions of open-source communities that provide high-quality software tools to people free of charge. My research relies on several open-source software, including QEMU, KVM, GDB, GCC, and Linux. I am also grateful to the software maintainers for taking the time to respond to the bug reports I submitted.

Finally, I would like to thank my family and friends for supporting me throughout this research. This long journey would not have been possible without you.

This research is self-funded.

